How Can We Open Plant Pathology?

### 2020-10-15 analysis/paper/paper.Rmd
Copy edits

Prefer text files for saving small sets of data.
Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._ comma separated (CSV) files.
This also helps ensure that the data are reusable.Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.

@@

Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.

@@

Readers should also consult with their local librarians about local resources.
Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories in some cases up as well.

>>>>

Prefer text files for saving small sets of data.
Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._ comma separated (CSV) files.
This also helps ensure that the data are reusable.
Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.

@@

Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
Providers such as FigShare, Dataverse, OSF.io (the Open Science Framework) and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.

@@

Readers should also consult with their local librarians about local resources.
Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
